\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64

### 2024-01-11 article.tex
Fix llivespans figure

Because of this, for any phi node of the form 
\begin{equation}
  a = \Phi (b_1, ..., b_n) \label{phi}
\end{equation}
add edges to all \textit{live-out} variables not in \(\{b_1, ..., b_n\}\)
\[
  \forall b_j \in \mathit{out}[i] \setminus \{b_1, ..., b_n\}, \text{add\_edge}(a, b_j),
\]
and for any other instruction that defines a variable \(a\)
\[
  \forall b_j \in \{b_1, ..., b_n\}, \text{add\_edge}(a, b_j).
\]
Although the Appel text \cite{tiger} describes interference of variables with concrete registers as well as overlapping variables, this isn't considered in this implementation % FIXME: why??
for simplicity's sake.

@@

\subsection{Heuristics spilling}
\usetikzlibrary{chains,arrows}
\begin{figure}[H]

     \centering
     \begin{minipage}[b]{0.30\textwidth}
     \centering

     \begin{tikzpicture}[scale=0.442,
    node distance=0mm, text height=1.5ex, text depth=.25ex,
    attribute/.style={rectangle,minimum size=8mm,very thin,draw=black!50,font=\ttfamily},
    link/.style={thin, to path={-- ++(0,8mm) -| (\tikztotarget)}, >= triangle 45, shorten >= 0pt}]

%\node (n1) [attribute] {\small NODE1};
%\node (n2) [attribute, right=of n1] {\small NODE2};

   \node at (7,0) (11) {};
   \node at (7,1) (10) {};
   \node at (7,2) (9) {};
   \node at (7,3) (8) {};
   \node at (7,4) (7) {};
   \node at (7,5) (6) {};
   \node at (7,6) (5) {};
   \node at (7,7) (4) {};
   \node at (7,8) (3) {};
   \node at (7,9) (2) {};

   \draw[|-|] (2)  node[above,transform canvas={xshift=1.43cm}] {\texttt{\%3}} edge [transform canvas={xshift=1.5cm}] (6);
   \draw[|-|] (3) node[above,transform canvas={xshift=0.83cm}] {\texttt{\%4}} edge [transform canvas={xshift=0.9cm}] (8);
   \draw[|-|] (4) node[above] {\texttt{\%5}} edge [ ]  (11);

@@

\end{tikzpicture}
\vspace{0.7em}
     \caption{Live ranges}\label{fig:linear.lra}
   \end{minipage}
   \begin{minipage}[b]{0.68\textwidth}
     \centering
     \begin{minted}[linenos,bgcolor=LightGray]{llvm}
define i32 @main (i32 %0, i8* %1) {
  %3 = getelementptr i8*, i8** %1, i64 1
  %4 = load i8*, i8** %3
  %5 = call i32 @atoi (i8* %4)
  call i32 @printf (i8* @.str, i8** %3, i8* %4, ...
  %7 = call i32 @isqrt (i32 %5)
  %8 = call i64 @strtoll (i8* %4, i8* null, i32 10)
  call i32 @printf (i8* @.str.1, i32 %5, i64 %8)
  call i32 @printf (i8* @.str.2, i32 %7, i32 %5)
  ret i32 %5
}
     \end{minted}
     \caption{\texttt{@main} of \texttt{tests/linear.ll}}\label{fig:linear.ll}
   \end{minipage}
\end{figure}

>>>>

Because of this, for any phi node of the form 
\begin{equation}
i a = \Phi (b_1, ..., b_n) \label{phi}
\end{equation}
add edges to all \textit{live-out} variables not in \(\{b_1, ..., b_n\}\)
\[
  \forall b_j \in \mathit{out}[i] \setminus \{b_1, ..., b_n\}, \text{add\_edge}(a, b_j),
\]
and for any other instruction that defines a variable \(a\)
\[
  \forall b_j \in \{b_1, ..., b_n\}, \text{add\_edge}(a, b_j).
\]
Although the Appel text \cite{tiger} describes interference of variables with concrete registers as well as overlapping variables, this isn't considered in this implementation % FIXME: why??
for simplicity's sake.

@@

\subsection{Heuristics spilling}
\usetikzlibrary{chains,arrows}
\begin{figure}[H]
    \centering
    \begin{minipage}[b]{0.31\textwidth}
      \centering
      \begin{tikzpicture}[scale=0.4]
        \node[above] at (0,0) {\texttt{\%3}};
        \node[above] at (1,-1) {\texttt{\%4}};
        \node[above] at (2,-2) {\texttt{\%5}};
        \node[above] at (3,-4) {\texttt{\%7}};
        \node[above] at (4,-5) {\texttt{\%8}};
        \draw[|-|] (0,0) edge   (0,-3);
        \draw[|-|] (1,-1) edge   (1,-5);
        \draw[|-|] (2,-2) edge   (2,-8);
        \draw[|-|] (3,-4) edge   (3,-7);
        \draw[|-|] (4,-5) edge   (4,-6);

@@

\end{tikzpicture}
\vspace{2.7em}
     \caption{Live intervals}\label{fig:linear.lra}
   \end{minipage}
   \begin{minipage}[b]{0.68\textwidth}
     \centering
     \begin{minted}[linenos,bgcolor=LightGray]{llvm}
define i32 @main (i32 %0, i8* %1) {
  %3 = getelementptr i8*, i8** %1, i64 1
  %4 = load i8*, i8** %3
  %5 = call i32 @atoi (i8* %4)
  call i32 @printf (i8* @.str, i8** %3, i8* %4, ...
  %7 = call i32 @isqrt (i32 %5)
  %8 = call i64 @strtoll (i8* %4, i8* null, i32 10)
  call i32 @printf (i8* @.str.1, i32 %5, i64 %8)
  call i32 @printf (i8* @.str.2, i32 %7, i32 %5)
  ret i32 %5
}
     \end{minted}
     \caption{\texttt{@main} of \texttt{tests/linear.ll}}\label{fig:linear.ll}
   \end{minipage}
\end{figure}
